Growing libraries of concepts with wake-sleep program induction

### 2018-10-02 pp.tex
probabilistic programming talk

\DeclareMathOperator*{\argmax}{arg\,max}
%Information to be included in the title page:
\title{Growing libraries of concepts with wake-sleep program induction}
\author{Kevin Ellis \& Mathias Sabl\'e Meyer\\Joint with: Lucas Morales, Armando Solar-Lezama, Joshua B. Tenenbaum\\Heavy inspiration from: Eyal Dechter}
\institute{MIT} 
%\date{November 2017}

@@

\begin{frame}{DreamCoder --- Sleep-G}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-g/slide-4.pdf}
  }
\end{frame}
\begin{frame}{DreamCoder --- Sleep-R (\textbf{Experience Replay})}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-r-1/slide-4.pdf}
  }
\end{frame}
\begin{frame}{DreamCoder --- Sleep-R (\textbf{Dreaming})}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-r-2/slide-4.pdf}
  }
\end{frame}

%% \begin{frame}[t]{Wake: Problem solving}
%%   \includegraphics[width = 11cm]{figures/animation/Wake.eps}

%%   \vfill
%%   \only<1>{
%%   Recognition model: Neural net.\\
%%   Red: Bottom-up inference.\\
%%   Gray: Observed.\\
%%   White: Latent.\\
%%   Boxed (plate): Repeated.\\
%%   }
%%   \only<2>{
%%   \begin{tikzpicture}[xscale=1.25,line width=1mm]
%%     \node at (0,0) (d){DSL};
%%     \node at ([yshift = -2cm]d) (t){$\text{Task}$};

%%     \node at ([xshift = 2cm]t) (nn){
%%       \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.3,shift={+(-1,2.5)}}]
%%        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
%%         \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
%%         \node[rectangle] at (1,1) {};
%%         \foreach \name / \y in {1,...,4}
%%             \node[neuron] (I-\name) at (0,-\y) {};
%%         \foreach \name / \y in {1,...,3}
%%             \node[neuron] (H-\name) at (1,-\y-0.5) {};
%%         \foreach \name / \y in {1,...,4}
%%             \node[neuron] (O-\name) at (2,-\y) {};
%%         \foreach \source in {1,...,4}
%%             \foreach \dest in {1,...,3}
%%                 \draw [-latex] (I-\source) -- (H-\dest);
%%         \foreach \source in {1,...,3}
%%             \foreach \dest in {1,...,4}
%%                 \draw [-latex] (H-\source) -- (O-\dest);
%%       \end{tikzpicture}
%%     };
%%     \node[align = center, text width = 1cm] at ([yshift = 0.7cm]nn.north) {\baselineskip=0pt \Small Recog. model\par};
%%     \draw [->] (t.east) -- ([xshift = -0.5cm]nn.west);

%%     \node[draw,rounded corners, inner sep = 10] at ([xshift = 4.2cm,yshift = -1cm]) (s){Search};
%% %    \node at ([xshift=-7pt,yshift=5pt]s.north west) {$\mathcal{D}$};

%%     \draw [->] ([xshift = 0.5cm]nn.east) -- ([yshift = -0.25cm]s.west);
%%     \draw [->,rounded corners] (d.east) -- ([yshift = 2cm]nn.center) -- ([yshift = 0.25cm]s.west);

%%     \node[align=left] at (7,-1) (f) {Programs};
%%     \draw [->  ] (s.east) -- (f.west);

%%     \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
%%   \end{tikzpicture}}
%%   %% Recognition model: Neural net.\\
%%   %% Red: Bottom-up inference.\\
%%   %% Gray: Observed.\\
%%   %% White: Latent.\\
%%   %% Boxed (plate): Repeated.\\

%% \end{frame}
%% \begin{frame}[t]{Sleep-G: Memory consolidation}
%%   \includegraphics[width = 11cm]{figures/animation/Sleep-G.eps}
%%   \vfill
%%   \textbf{Fragment Grammars: O'Donnell 2015.}\\
%%   Orange: Code fragments.\\
%%   %% Gray: Observed.\\
%%   %% White: Latent.\\
%%   %% Boxed (plate): Repeated.\\

%% \end{frame}
%% \begin{frame}[t]{Sleep-R: Objective}
%%   \includegraphics[width = 11cm]{figures/animation/Wake.eps}

%%     \vfill
%%     Recognition model predicts distribution over program, conditional on task.\\
%%     Training: (program, task) pairs\\
%%     Objective: Predict program w/ (1) high prior under DSL \& \\(2) high likelihood for task

%% \end{frame}
%% \begin{frame}[t]{Sleep-R: Experience replay}
%%   \includegraphics[width = 11cm]{figures/animation/Sleep-R-1.eps}

%%     \textbf{Train on (program, task) pairs found during waking}
%% \end{frame}
%% \begin{frame}[t]{Sleep-R: Dreaming}
%%   \includegraphics[width = 11cm]{figures/animation/Sleep-R-2.eps}

%%     \textbf{Train on (program, task) pairs sampled from DSL}

%% \end{frame}

@@

  Discovers 38 concepts, including `filter'. With suitable curriculum can also learn `map', `fold', etc. starting with 1950's Lisp
\end{frame}

\begin{frame}{List functions \& Text editing: Learning curves on hold out tasks}

@@

%% \begin{frame}{Text editing}
%%   In the style of FlashFill (Gulwani 2012)

%%   \centering  \includegraphics[width = 5cm]{textColumn.png}

%%   SyGuS problems: solves 3\% before learning, vs 74\% after learning. Best prior work: 80\%

%%   \end{frame}

%% \begin{frame}{Symbolic regression from visual input}
%% \centering\includegraphics[width = 5cm]{symbolicRegression.png}
%% \end{frame}

@@

  \only<1>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \vspace*{5\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/line.eps}
    \end{columns}
  }
  \only<2>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle.eps}
    \end{columns}
  }
  \only<3>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{1\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle2.eps}
    \end{columns}
  }
  \only<4>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(4)}\\
          \texttt{> FW 1}\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/square.eps}
    \end{columns}
  }
  \only<5>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> FW 1} \\
          \texttt{> SET origin} \\
          \texttt{> RT} $\frac{2\pi}{8}$\\
          \vspace*{2\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/star.eps}
    \end{columns}
  }
  \only<6>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> PU} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> PD} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{0\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/spiral.eps}
    \end{columns}
  }
  \only<7>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range($\infty$)}\\
          \texttt{> FW $\varepsilon$}\\
          \texttt{> RT} $\varepsilon$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/circle.eps}
    \end{columns}
  }
  \only<8-9>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range($5\times\infty$)}\\
          \texttt{> FW $\text{\texttt{i}}\times\varepsilon$}\\
          \texttt{> RT} $\varepsilon$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/sspiral.eps}
    \end{columns}
  }
  \visible<9>{
    \vspace{0.2cm}
    \texttt{\alert{NUM} ::= 1 | $\pi$ | $\infty$ | $\varepsilon$ | + | - | * | / }
  }
\end{frame}

@@

\begin{frame}{Turtle graphics --- Generative model}
  \centering
  \only<1>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/1.png}
    \end{figure}
  }
  \only<2>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/2.png}
    \end{figure}
  }
  \only<3>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/3.png}
    \end{figure}
  }
  \only<4>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/4.png}
    \end{figure}
  }
  \only<5>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/6.png}
    \end{figure}
  }
  \only<6>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/7.png}
    \end{figure}
  }
  \only<7>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/8.png}
    \end{figure}
  }
  \only<8>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/9.png}
    \end{figure}
  }
\end{frame}

\begin{frame}{Turtle graphics --- All the way down}
  \centering
  \begin{center}
  \only<1>{
  \begin{tikzpicture}
      \node at(-10,0) {\includegraphics[width=5cm]{figures/marieSequences.png}};
      \node at(-4,0) {\includegraphics[width=5cm]{figures/teachLogo/star5_black.eps}};
    \node at (-10,-4) {Marie Amalric, Stanislas Dehaene et al.};
    \end{tikzpicture}
  }
  \only<2>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_colour.eps}
    \end{figure}
  }
  \only<3>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq1.eps}
    \end{figure}
  }
  \only<4>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq2.eps}
    \end{figure}
  }
  \only<5>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq3.eps}
    \end{figure}
  }
  \only<6>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq4.eps}
    \end{figure}
  }
  \only<7>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq5.eps}
    \end{figure}
  }
  \only<8>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq1.eps}
    \end{figure}
  }
  \only<9>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq2.eps}
    \end{figure}
  }
  \only<10>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq3.eps}
    \end{figure}
  }
  \only<11>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq4.eps}
    \end{figure}
  }
  \only<12>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq5.eps}
    \end{figure}
  }
  \only<13>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/star5_seq1.eps}
    \end{figure}
  }
  \only<14>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp000.png}
    \end{figure}
  }
  \only<15>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp002.png}
    \end{figure}
  }
  \only<16>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp004.png}
    \end{figure}
  }
  \only<17>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp006.png}
    \end{figure}
  }
  \only<18>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp008.png}
    \end{figure}
  }
  \only<19>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp010.png}
    \end{figure}
  }
  \only<20>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp012.png}
    \end{figure}
  }
  \only<21>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp014.png}
    \end{figure}
  }
  \only<22>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp016.png}
    \end{figure}
  }
  \only<23>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp018.png}
    \end{figure}
  }
  \only<24>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp020.png}
    \end{figure}
  }
  \only<25>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp022.png}
    \end{figure}
  }
  \only<26>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp024.png}
    \end{figure}
  }
  \only<27>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp026.png}
    \end{figure}
  }
  \only<28>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp028.png}
    \end{figure}
  }
  \only<29>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp030.png}
    \end{figure}
  }
  \only<30>{
    \begin{figure}
    \includegraphics[width=5cm]{figures/teachLogo/spiral/seqSp032.png}
    \end{figure}
  }
\end{center}
\end{frame}

@@

   \underline{More human-like machine intelligence}\\%Flexibly adapting to new problem domains:
   \begin{itemize}
   \item    Acquiring a domain-specific language-of-thought (DSL)
     \item Learning  to use the language of thought (recognition model)
   \end{itemize}
   DreamCoder: an algorithm for jointly realizing these goals

>>>>

\DeclareMathOperator*{\argmax}{arg\,max}
%Information to be included in the title page:
\title{Growing libraries of concepts with wake-sleep program induction}
\author{Kevin Ellis\\Joint with: Lucas Morales, Mathias Sabl\'e Meyer, Armando Solar-Lezama, Joshua B. Tenenbaum\\Heavy inspiration from: Eyal Dechter}
\institute{MIT} 
\date{October 2018}

@@

\begin{frame}{DreamCoder --- Sleep-G}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-g/slide-4.pdf}
  }
\end{frame}

\begin{frame}{DreamCoder --- Sleep-G (\textbf{Refactoring})}
  \textbf{Learning higher-order \texttt{map} function}

  \begin{tabular}{cc}
    \toprule Task&Program\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2 3)}$\to$\texttt{(2 4 6)}\\
      \texttt{(1 9 2)}$\to$\texttt{(2 18 4)}\\
    \end{tabular}&

    \begin{tabular}{l}
      \texttt{(Y ($\lambda$ (r l) (if (nil? l) nil}\\
      \texttt{ (cons (+ (car l) (car l))}\\
      \phantom{\texttt{(cons }}\texttt{ (r (cdr l))))))}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2 3)}$\to$\texttt{(2 3 4)}\\
      \texttt{(1 9 2)}$\to$\texttt{(2 10 3)}\\
    \end{tabular}&
    \begin{tabular}{l}
      \texttt{(Y ($\lambda$ (r l) (if (nil? l) nil}\\
      \texttt{ (cons (+ (car l) 1)}\\
      \phantom{\texttt{(cons }}\texttt{ (r (cdr l))))))}
    \end{tabular}

    \\\bottomrule
  \end{tabular}

     \visible<2->{
      \centering
      \begin{tabular}{l}
          \texttt{\emph{map}} = \orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(cons (f (car l))}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(r (cdr l))))))}}
      \end{tabular}
}
\end{frame}

\begin{frame}{DreamCoder --- Sleep-G (\textbf{Refactoring})}
  \textbf{Learning higher-order \texttt{map} function}

  \begin{tabular}{cc}
    \toprule Task&Program\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2)}$\to$\texttt{(2 4)}\\
      \texttt{(1 9)}$\to$\texttt{(2 18)}\\
    \end{tabular}&
\begin{tabular}{l}
\texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z z)))}
      \end{tabular}

    \begin{tabular}{l}
    \end{tabular}\\\midrule
    \begin{tabular}{l}
      \texttt{(1 2)}$\to$\texttt{(2 3)}\\
      \texttt{(1 9)}$\to$\texttt{(2 10)}\\
    \end{tabular}&
    \begin{tabular}{l}
\begin{tabular}{l}
\texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z 1)))}
      \end{tabular}
    \end{tabular}

    \\\bottomrule
  \end{tabular}

      \centering
\begin{tabular}{l}
          \texttt{\emph{map}} = \orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(cons (f (car l))}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(r (cdr l))))))}}
      \end{tabular}

\begin{frame}[plain]{}\footnotesize
  \Wider[5.4em]{
    \begin{tikzpicture}[every node/.style={inner sep=0,outer sep=0}]
    \node(p1)[draw] at (-1,0) {
      \begin{tabular}{l}
      \texttt{(Y ($\lambda$ (r l) (if (nil? l) nil}\\
      \texttt{ (cons (+ (car l) (car l))}\\
      \phantom{\texttt{(cons }}\texttt{ (r (cdr l))))))}
    \end{tabular}
    };
    \node(r1)[draw,inner sep=0,outer sep=0] at ([yshift=-3cm]p1.south) {
      \begin{tabular}{l}
  \texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l)}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{ (r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z z)))}
      \end{tabular}
    };

        \node(p2)[draw] at ([xshift=3.5cm]p1.east) {
    \begin{tabular}{l}
      \texttt{(Y ($\lambda$ (r l) (if (nil? l) nil}\\
      \texttt{ (cons (+ (car l) 1)}\\
      \phantom{\texttt{(cons }}\texttt{ (r (cdr l))))))}
    \end{tabular}

    };
    \node(r2)[draw] at ([yshift=-3cm]p2.south) {
\begin{tabular}{l}
  \texttt{(}\orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l)}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{nil}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{(cons (f (car l))}}\\
\phantom{(($\lambda$ (f) (Y ($\lambda$ (r l)}\orange{\texttt{ (r (cdr l)))))))}}\\
\texttt{ ($\lambda$ (z) (+ z 1)))}
      \end{tabular}

    };

    \draw [->] (p1.south)  --(r1.north) node[fill=white,midway] {refactor};
    \draw [->] (p2.south)  --(r2.north) node[fill=white,midway] {refactor};

    \node[draw](m) at (2,-7) {
\begin{tabular}{l}
          \texttt{\emph{map}} = \orange{\texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if (nil? l) nil}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(cons (f (car l))}}\\
  \phantom{\texttt{\emph{map}} = \texttt{($\lambda$ (f) (Y ($\lambda$ (r l) (if }}\orange{\texttt{(r (cdr l))))))}}
      \end{tabular}      
    };
    \draw [->](r1.south)--(m.north);
    \draw [->](r2.south)--(m.north);
    \node[fill=white] at ([yshift=0.5cm]m.north) {\textbf{Compress (MDL/Bayes objective)}};
    \visible<2-3>{
      \node[fill=orange!50!white,align=center] at (r1) {\Huge $10^{14}$\\\Huge  refactorings };
      \node[fill=orange!50!white,align=center] at (r2) {\Huge $10^{13}$\\\Huge  refactorings };
    }
    \visible<3>{
      \node[fill=orange!50!white,align=center] at ([yshift=7cm]m.north) {\Huge version space: set of programs\\
      \huge Lau 2003; Gulwani 2012};
      }
    \visible<4>{
      \node[fill=orange!50!white,align=center] at (r1) {\Huge $\leq 10^6$\\\Huge version spaces };
      \node[fill=orange!50!white,align=center] at (r2) {\Huge $\leq 10^6$\\\Huge version spaces };
    }
    \end{tikzpicture}
    }
  \end{frame}

\begin{frame}{DreamCoder --- Sleep-R (\textbf{Experience Replay})}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-r-1/slide-4.pdf}
  }
\end{frame}
\begin{frame}{DreamCoder --- Sleep-R (\textbf{Dreaming})}
  \only<1>{
    \includegraphics[width=11cm]{figures/teachDC/.inkslides-sleep-r-2/slide-4.pdf}
  }
\end{frame}

@@

  Discovers 38 concepts, including `filter'. With different tasks will also learn `map', `fold', `unfold', etc. starting with 1950's Lisp
\end{frame}

\begin{frame}{Text editing}
  In the style of FlashFill (Gulwani 2012)

  \centering  \includegraphics[width = 5cm]{textColumn.png}

\vspace{-0.5cm}  SyGuS problems: solves 3\% before learning, vs 75\% after learning. Best prior work: 80\%

\end{frame}
\begin{frame}{List functions \& Text editing: Learning curves on hold out tasks}

@@

\begin{frame}{Symbolic regression from visual input}
\centering\includegraphics[width = 5cm]{symbolicRegression.png}
\end{frame}

@@

  \only<1>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \vspace*{5\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/line.eps}
    \end{columns}
  }
  \only<2>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle.eps}
    \end{columns}
  }
  \only<3>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{1\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle2.eps}
    \end{columns}
  }
  \only<4>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(4)}\\
          \texttt{> FW 1}\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/square.eps}
    \end{columns}
  }
  \only<5>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> FW 1} \\
          \texttt{> SET origin} \\
          \texttt{> RT} $\frac{2\pi}{8}$\\
          \vspace*{2\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/star.eps}
    \end{columns}
  }
  \only<6>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> PU} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> PD} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{0\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/spiral.eps}
    \end{columns}
  }
  \only<7>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range($\infty$)}\\
          \texttt{> FW $\varepsilon$}\\
          \texttt{> RT} $\varepsilon$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/circle.eps}
    \end{columns}
  }
  \visible<7>{
    \vspace{0.2cm}
    \texttt{\alert{NUM} ::= 1 | $\pi$ | $\infty$ | $\varepsilon$ | + | - | * | / }
  }
\end{frame}

@@

\begin{frame}{Turtle graphics --- Dreaming from learned generative model}
  \centering
  \only<1>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/1.png}
    \end{figure}
  }
  \only<2>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/2.png}
    \end{figure}
  }
  \only<3>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/3.png}
    \end{figure}
  }
  \only<4>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/4.png}
    \end{figure}
  }
  \only<5>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/6.png}
    \end{figure}
  }
  \only<6>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/7.png}
    \end{figure}
  }
  \only<7>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/8.png}
    \end{figure}
  }
  \only<8>{
    \begin{figure}
      \includegraphics[width=6cm]{figures/dreams/9.png}
    \end{figure}
  }
\end{frame}
\begin{frame}{Tower building in blocks world}
  \large
\centering  
  Control a hand that puts down blocks \\
  \hspace{1cm}(turtle: control a pen that puts down ink)
\only<1>{\includegraphics[width = \textwidth]{figures/3t.png}}
\only<2>{\includegraphics[width = 0.6\textwidth]{figures/every_tower.png}}

\begin{frame}{Tower building in blocks world: Learned concepts}
  Parametric planning primitives. Example pyramid concept:

  \includegraphics[width = \textwidth]{figures/pyramid.png}

\begin{frame}{Tower building in blocks world: Learned concepts}
  Parametric planning primitives. Example brickwall concept:

  \includegraphics[width = \textwidth]{figures/brickwall.png}

@@

   \underline{More human-like machine intelligence}\\%Flexibly adapting to new problem domains:
   \begin{itemize}
   \item    Acquiring a domain-specific representation (DSL)
     \item Learning  to write programs (recognition model)
   \end{itemize}
   DreamCoder: an algorithm for jointly realizing these goals
